Paper 1

### 2022-05-24 scripts/Paper 1.Rmd
add rainfall data

```{r Precipitation, echo=FALSE, message = FALSE, fig.width = 10, fig.height = 4}
# this is the rainfall data for Interlaken estate, but there is a lot missing so results are probably underestimated
# need to uodate this each month or so from BOM website
input.bom.rain <- read.csv("R:/SET/PlantSci/Shared Work Spaces/Ecology/Peoples files/Marion Nyberg/PhD/SP warming experiment/Interlaken_BOM_rainfall.csv") %>% filter(Year >= 2019)
  #filter(Year >= 2010 & Year <= 2019) %>% # used all years available due to missing data 1995 - 2021
  select(Year, Month, Day, Rainfall.amount..millimetres.) %>%
  mutate(Precip = replace_na(Rainfall.amount..millimetres., 0)) %>%
  ddply(c("Year", "Month"), summarise,
  monthly.total = sum(Precip)) %>%
  ddply(c("Month"), summarise,
        monthly.total = mean(monthly.total)) 
names(input.bom.rain)[1] <- "month"
input.bom.rain$Year <- "BOMavg"

input.daily %>% mutate(Precip = replace_na(Precip, 0)) %>%
  ddply(c("Year", "month"), summarise,
  monthly.total = sum(Precip)) %>%
  ggplot(., aes(x = month, y = monthly.total, group = Year, fill = Year)) +
       scale_x_discrete(limits = month.abb) +
  geom_col(position = "dodge") + 
  ylab("Monthly rainfall (mm)")+
  xlab("Month")+
  theme_classic()
```

>>>>

```{r Precipitation, echo=FALSE, message = FALSE, fig.width = 10, fig.height = 4}
input.daily %>% mutate(Precip = replace_na(Precip, 0)) %>%
  ddply(c("Year", "month"), summarise,
  monthly.total = sum(Precip)) %>%
  ggplot(., aes(x = month, y = monthly.total, group = Year, fill = Year)) +
       scale_x_discrete(limits = month.abb) +
  geom_col(position = "dodge") + 
  ylab("Monthly rainfall (mm)")+
  xlab("Month")+
  theme_classic()

#below is precip data from liaweenee - it only goes up to Jan 2022 right now
rainfall_L <- read.csv("R:/SET/PlantSci/Shared Work Spaces/Ecology/Peoples files/Marion Nyberg/PhD/Rainfall/rainfall.csv")
rainfall_L <- rainfall_L[-1]
colnames(rainfall_L)[4] <- "Precip"
rainfall_L$Year <- as.factor(rainfall_L$Year)

rainfall_L %>% mutate(Precip = replace_na(Precip, 0)) %>%
  ddply(c("Year", "Month"), summarise,
  monthly.total = sum(Precip)) %>%
  ggplot(., aes(x = Month, y = monthly.total, group = Year, fill = Year)) +
       scale_x_discrete(limits = month.abb) +
  geom_col(position = "dodge") + 
  ylab("Monthly rainfall (mm)")+
  xlab("Month")+
  theme_classic()
